XXXXX \todo{Le titre !} XXXXX

### 2013-03-19 parts/def-ph.tex
update defs

We define the set of chains of actions $\PHh(b, a)$ between two sorts $b$ and $a$ as below:
\begin{align*}
\PHh(b, a) = \{ (h_i)_{i \in \segm{0}{s}} \in (\restriction{\PHh}{\prio(b)})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = b \wedge \PHsort(\PHtarget(h_n)) = a \\
  & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i-1})) = \PHsort(\PHhitter(h_{i})) \}
\end{align*}

We define the neighbor \towrite{Revoir terminologie : “neighborhood” ? “vicinity” ?} sorts of any sort $a$ as :
$$
\Vs(a) = \{ b \in \PHs \mid \PHh(b, a) \neq \emptyset \}
$$

@@

\paragraph{Cycle-freeness of $\restriction{\PH}{k-1}$}
\towrite{Définition formelle ? + justification}
The model $\restriction{\PH}{k-1}$ contains no cycles. Cycles are still allowed in $\PH$ however.

@@

\pref{th:vplay} tells that for any action $h = \PHhit{a_i}{b_j}{b_k}$, if no action can be played in the neighborhood of $a$ in a given state, then $h$ can be played after a series of hits that do not prevent it to be fired. Furthermore, if the requisites of \pref{th:vplay} are true, then no action of this series of hits belongs to $V(a)$, as stated in \pref{co:vplay}.
\begin{theorem}
\label{th:vplay}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
  $\forall h' \in \Vh(a), \PHsort(\PHtarget(h')) \neq a \Rightarrow \text{$h'$ cannot be played in $s$}) \Rightarrow$\\
  $(\exists \delta \in \Sce, \text{$h$ can be played in $s \PHplay \delta$})$
\end{theorem}

@@

\begin{corollary}
  \label{co:vplay}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
  $(\forall h' \in \Vh(a), \PHsort(\PHtarget(h')) \neq a \Rightarrow \text{$h'$ cannot be played in $s$}) \Rightarrow$\\
  $\exists \delta \in \Sce, (\forall n \in \indexes{\delta}, \forall h' \in \delta_n, \PHsort(\PHtarget(h')) \notin \Vh(a)) \wedge (\text{$h$ can be played in $s \PHplay \delta$})$
\end{corollary}

\pref{th:totalss} states that from any state, a steady state is eventually reached. A local variant of this theorem, given in \pref{co:totalss}, can be derived,
where, for all $\Omega \subset \PHs$, $$\restriction{\PHl}{\Omega} = \underset{a \in \Omega}{\times} \PHl_a$$ and
for all $H \subset \PHh$, $$\restriction{\Sce}{H} = \{ \delta \in \Sce \mid \forall n \in \indexes{\delta}, \delta_n \in H \} \enspace .$$
\begin{theorem}
\label{th:totalss}
  $\forall s \in \PHl, \exists \delta \in \Sce$, no action can be played in $s \PHplay \delta$.
\end{theorem}

\begin{corollary}
\label{co:totalss}
  $\forall a \in \PHs, \forall s \in \restriction{\PHl}{V(a)}, \exists \delta \in \restriction{\Sce}{V(a)}$, no action can be played in $s \PHplay \delta$.
\end{corollary}

>>>>

We define the set of chains of actions $\PHh^n(b, a)$ between two sorts $b$ and $a$, with $n \in \segm{1}{k}$, as below:
\begin{align*}
\PHh^n(b, a) = \{ (h_i)_{i \in \segm{0}{s}} \in (\restriction{\PHh}{n})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = b \wedge \PHsort(\PHtarget(h_s)) = a \\
  & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i-1})) = \PHsort(\PHhitter(h_{i})) \}
\end{align*}

We define the neighbor \towrite{Revoir terminologie : “neighborhood” ? “vicinity” ?} sorts of any sort $a$ and $n \in \segm{1}{k}$ as :
$$
\Vs^n(a) = \{ b \in \PHs \mid \PHh^m(b, a) \neq \emptyset \wedge m = \min(n, \prio(a)) \}
$$

And, as a shortcut:
$$
\Vs(a) = \Vs^{\prio(a)}(a)
$$

@@

%\paragraph{Cycle-freeness of $\restriction{\PH}{k-1}$}
%\towrite{Définition formelle ? + justification}
%The model $\restriction{\PH}{k-1}$ contains no cycles. Cycles are still allowed in $\PH$ however.

\paragraph{Bounded reachability property}
The dynamics of model $\restriction{\PH}{k-1}$ contains no cycles. Cycles are still allowed in $\PH$ however.
Formally : $\exists N \in \sN, \forall \delta \in \restriction{\Sce}{k-1}, |\indexes{\delta}| \leq N$.

@@

\pref{th:vplay} tells that for any action $h = \PHhit{a_i}{b_j}{b_k}$, if no action can be played in the neighborhood of $a$ in a given state, then $h$ can be played after a series of hits that do not prevent it to be fired. Furthermore, if the requisites of \pref{th:vplay} are true, then no action of this series of hits belongs to $V(a)$, as stated in \pref{co:vplay}.
\begin{theorem}
\label{th:vplay}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
  $\forall h' \in \Vh(a), \text{$h'$ cannot be played in $s$}) \Rightarrow (\exists \delta \in \Sce, \text{$h$ can be played in $s \PHplay \delta$})$
\end{theorem}

@@

\begin{corollary}
  \label{co:vplay}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
  $(\forall h' \in \Vh(a), \text{$h'$ cannot be played in $s$}) \Rightarrow$\\
  $\exists \delta \in \Sce, (\forall n \in \indexes{\delta}, \delta_n \notin \Vh(a)) \wedge (\text{$h$ can be played in $s \PHplay \delta$})$
\end{corollary}

\pref{th:totalss} states that from any state, a steady state is eventually reached. A local variant of this theorem, given in \pref{co:totalss}, can be derived,
where, for all $\Omega \subset \PHs$, $$\restriction{\PHl}{\Omega} = \underset{a \in \Omega}{\times} \PHl_a$$ and
for all $H \subset \PHh$, $$\restriction{\Sce}{H} = \{ \delta \in \Sce \mid \forall n \in \indexes{\delta}, \delta_n \in H \} \enspace .$$
\begin{theorem}
\label{th:totalss}
  $\forall n \in \segm{1}{k-1}, \forall s \in \PHl, \exists \delta \in \restriction{\Sce}{n}$, no action of model $\restriction{\PH}{n}$ can be played in $s \PHplay \delta$.
\end{theorem}

\begin{corollary}
\label{co:totalss}
  $\forall a \in \PHs, \forall s \in \restriction{\PHl}{\Vs(a)}, \exists \delta \in \restriction{\Sce}{\Vh(a)}$, no action of $\Vh(a)$ can be played in $s \PHplay \delta$.
\end{corollary}

### 2013-03-19 parts/sa.tex
update defs

Approximation : pour qu'une séquence de bonds soit jouable, il faut pouvoir atteindre tous les processus nécessaires depuis tous les points fixes possibles locaux, uniquement à l'aide d'actions de priorité maximale pour la sorte considérée.

@@

\begin{definition}
  \label{def:aS}
  The abstract structure $\cwB=(\Breq,\Bsol,\Bcont,\Bsat)$ is defined as
  $
  \cwB = \sfp{\myB}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}
  $,
  with $\myB=(\myreq,\mysol,\mycont,\mysat)$:
  \begin{align*}
    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
      a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
      & \qquad \wedge (\exists (P,ps) \in \mysol, a_i \in ps \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
    \\
    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
      & \qquad\qquad \exists (Q, P) \in \myreq \cup \mysat \wedge ps \in \aBS(P) \}
    \\
    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
      \exists (P, ps) \in \mysol \\
      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
    \\
    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
      \exists (a_i, \PHobjp{a}{j}{i}) \in \myreq, \\
      & \qquad\qquad a_j \neq a_k \wedge a_j \in \pfpprocs_\ctx(a) \\
      & \qquad\qquad \wedge (\exists (P, ps) \in \mysol, a_j \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
      & \qquad\qquad\qquad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \mysol, \exists p \in ps, \exists (p, P) \in \myreq,\\
      & \qquad\qquad\qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
  \end{align*}
\end{definition}

>>>>

@@

\begin{definition}
  \label{def:aS}
  The abstract structure $\cwB=(\Breq,\Bsol,\Bcont,\Bsat)$ is defined as
  $
  \cwB = \sfp{\myB}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}
  $,
  with $\myB=(\myreq,\mysol,\mycont,\mysat)$:
  \begin{align*}
    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
      a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
      & \qquad \wedge (\exists (P,ps) \in \mysol, a_i \in ps \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
    \\
    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
      & \qquad\qquad \exists (Q, P) \in \myreq \cup \mysat \wedge ps \in \aBS(P) \}
    \\
    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
      \exists (P, ps) \in \mysol \\
      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
    \\
    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
      \exists (a_i, \PHobjp{a}{j}{i}) \in \myreq, \\
      & \qquad\qquad a_j \neq a_k \wedge a_k \in \pfpprocs_\ctx(a) \\
      & \qquad\qquad \wedge (\exists (P, ps) \in \mysol, a_j \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
      & \qquad\qquad\qquad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \mysol, \exists p \in ps, \exists (p, P) \in \myreq,\\
      & \qquad\qquad\qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
  \end{align*}
\end{definition}
